Subject-specific curves for time series forecasting of smart meter demand

### 2019-11-25 sscts-paper-1.Rmd
Fix decimal scale for plot. Changed to integers.

```{r fs-model-selection, fig.cap = "(ref:fs-model-selection)"}
fs_df %>%
  select(month, period, features) %>%
  unnest() %>%
  select(month, period, n_vars, loocv) %>%
  mutate(month = month(month, label = TRUE)) %>%
  ggplot(aes(y = loocv, x = n_vars, colour = period, group = period)) +
  geom_line(alpha = 0.5) +
  facet_wrap(~month) +
  scale_colour_gradient2(low = ba_palette[1], mid = ba_palette[4],
                         high = ba_palette[2], midpoint = 48) +
  labs(
    x = "Number of variables",
    y = "LOOCV scores",
    colour = "Period"
  )
```

>>>>

```{r fs-model-selection, fig.cap = "(ref:fs-model-selection)"}
fs_df %>%
  select(month, period, features) %>%
  unnest() %>%
  select(month, period, n_vars, loocv) %>%
  mutate(month = month(month, label = TRUE)) %>%
  ggplot(aes(y = loocv, x = n_vars, colour = period, group = period)) +
  geom_line(alpha = 0.5) +
  facet_wrap(~month) +
  scale_colour_gradient2(low = ba_palette[1], mid = ba_palette[4],
                         high = ba_palette[2], midpoint = 48) +
  labs(
    x = "Number of variables",
    y = "LOOCV scores",
    colour = "Period"
  ) + 
  scale_x_continuous(breaks=c(0,3,6,9,12))
```
